% !TEX program = xelatex
\documentclass[12pt, a4paper]{yp-vita}
\geometry{top=0.6in, bottom=0.6in, right=0.8in, left=0.8in}

\name{Yihua}{Pu}
\mobile{+1 562-741-9089}
\email{puyihua1@gmail.com}
\github{github.com/puyihua}
\linkedin{linkedin.com/in/puyh/}
\begin{document}
    \makename
    \makecontact{\myemail}{\mymobile}{\mygithub}{\mylinkedin}
    \medskip
    \msection{Education}

    \mentry
        {Carnegie Mellon University}
        {Master of Science in Electrical and Computer Engineering (ECE)}
        {May 2022}
        {
            \begin{cvitems}
                \item {Coursework: Foundations of Computer Systems, Machine Learning in Production}
            \end{cvitems}
        }
    \smallskip

    \mentry
        {University of Illinois at Chicago (UIC)}
        {One-year Exchange Program at ECE Department}
        {May 2019}
        {
            \begin{cvitems} % Description(s) bullet points
              \item {GPA: 4.00 / 4.00}
              \item {Coursework: Operating System Design \& Implementation, Computer Organization, Software Design, Programming Language Design, Pattern Recognition}
            \end{cvitems}
          }
    
    \smallskip

    \mentry
        {East China University of Science and Technology (ECUST)}
        {Bachelor of Engineering in Electrical Engineering}
        {July 2019}
        {
            \begin{cvitems} % Description(s) bullet points
                \item {Ranking: 1 / 61;~~~~Overall GPA: 3.84 / 4.00;~~~~Major GPA: 3.95 / 4.00}
                \item {Coursework: C, Python, Discrete Math, Data Structure \& Algorithms, Software Engineering, Database, Artificial Intelligence, Optimization Methods, Embedded System}
            \end{cvitems}
        }
    
    \vfill
    \msection{Work Experience}

    \mentry{Apple}
    {Software Engineering Intern}
    {Mar. 2020 - Sept. 2020}
    {
        \begin{cvitems}
            \item Worked on an initiative to centralize and optimize the palletization process. 
            \item Developed an iPad App using \textbf{Swift} that integrated with SAP Cloud and on-premise SAP system.
            \item Built a game that gamifies the palletization process for learning and training using \textbf{Unity} and \textbf{C\#}.
            \item Worked with a matrix team distributed across locations (Shanghai, Singapore, US); presented to senior executives.
        \end{cvitems}
    }

    \smallskip

    \mentry{eBay}
    {Software Engineering Intern}
    {Oct. 2019 - Mar. 2020}
    {
        \begin{cvitems}
            \item Participated in agile development and contributed 20+ new features to the Financial Accounting System that processes all the transactions of eBay.
            \item Created \textbf{RESTful APIs} with \textbf{Java Spring} and web pages with \textbf{React}; managed projects with \textbf{Maven}.
            \item Built a set of \textbf{Python} scripts to automate repetitive tasks, such as journal validation and data fixing.
        \end{cvitems}
    }

    \smallskip

    \mentry{Renlifang Intelligent Tech}
    {Software Engineering Intern}
    {July 2018 - Aug. 2018}{
        \begin{cvitems}
            \item Worked on data collection for a stock analysis system that estimates the risk of trading strategies.
            \item Designed and implemented a pipeline to crawl, clean, format, and store about 43 million stock records using \textbf{Python Scrapy} and \textbf{MySQL}.
        \end{cvitems}
    }
    
    \vfill
    \msection{Projects}

    \mentry{Electroencephalography (EEG) Classification using Deep Learning}
    {Research Assistant}{}{
        \begin{cvitems}
            \item Implemented a Convolutional Neural Network (\textbf{CNN}) to classify EEG signals and predict which character was stared at by disabled subjects.
            \item Trained this network using \textbf{Python Keras} and achieved 91\% test accuracy on the BCI Competition III dataset, which outperformed tradition LDA methods by 8\%.
        \end{cvitems}
    }

    \smallskip

    \mentry{
        \href{https://github.com/puyihua/OS-Design-Implem-Projects/}{Operating System Core Functions Implementation}
    }{UIC CS461 Project}{}{
        \begin{cvitems}
            \item Built OS functions in XV6 (a Unix-like x86 OS) using C and X86 Assembly, debugged with GDB.
            \item Implemented Functions: bootloader, console driver, graphics driver, memory and page management, `/proc` virtual file.
        \end{cvitems}
    }

    \vfill
    \msection{Skills}

    \skillentry
        {Programming}
        {C, C++, C\#, C\#+, JavaScript, JavaPaper, JavaTissue, Matlab, Python, Snake}

    \skillentry
        {Framework / Library}
        {Spring Boot, JUnit, React, Express, Django, Scrapy, Keras, NumPy, Unity}
    
    \skillentry
        {DevOps}
        {Maven, Git, Docker, Kubernetes, Jenkins, AWS}
    
\end{document}